On the adhesivity of EGGS

### 2025-02-23 calco/Labeled_hyp_with_eq.tex
minima

>>>>

We can lift the adjunction given by $T$ and $L$ to $EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}

By \Cref{cor:mono1}, we can deduce what follows.

\begin{proposition}\label{prop:monos_in_eqhyps}
	A morphism $h$ between two objects of $\EqHyps$ is mono if and only if $T(h)$ is mono.
\end{proposition}
